Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-15 icse/paper.tex
Added contents table

>>>>

\begin{table}[H]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
Category & Contents & Clone instances & Total \\ \midrule
\multirow{2}{*}{Partial} & Partial Method & 219,540 & 229,521 \\
 & Partial Constructor & 9,981 &  \\
Full & Full Method & 12,990 & 13,173 \\
 & Full Interface & 64 &  \\
 & Full Constructor & 58 &  \\
 & Full Class & 37 &  \\
 & Full Enum & 24 &  \\
Other & Several Methods & 22,749 & 53,773 \\
 & Only Fields & 17,700 &  \\
 & Other & 13,324 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone instances for clone contents categories}
\label{tab:contents}
\end{table}
